%!TEX root = ttc16-cra-sigma.tex

\section{Evaluation}
\label{sec:Evaluation}
\enlargethispage{10mm}

In this section we provide an evaluation of our solution following the categories given by the case study description.
We leave the complexity and flexibility characteristics to be evaluated by reviewers.
All the presented results are based on the NSGA-III algorithm which in all runs performed better than SPEA2. 
More results are provided on the github page.

\Paragraph{Completeness \& Correctness}
The solution always converts a valid input RDG into a class model.
The three constraints that were imposed by the solution description are solved as follows:
%
\begin{compactitem}[---]
  \item \emph{Every class must have a unique name.} 
  The new classes are created in a loop that iterates over a number range.
  Part of the class name is the iteration variable and thus it must be always unique.
  \item \emph{All features provided in the input model must be encapsulated by a class.} 
  This has been already explained in the previous section.
  This is a property of the problem mapping we have chosen.
  \item \emph{There cannot be any empty classes.}
  We explicitly filter out empty classes.
\end{compactitem}

\Paragraph{Optimality and Performance}
The following table shows the cohesion and coupling rations, the resulting CRA-Index as well as the completion time from the SHARE environment\footnote{These are the initial results submitted for the competition. Improved result obtained after a better use of parallelism and better crossover and mutation ratios are available at \url{https://github.com/fikovnik/ttc16-cra-sigma}}:
\begin{center}
\begin{tabular}{crrrr}
\hline
\textbf{Input} & \textbf{Cohesion} & \textbf{Coupling} & \textbf{CRA} & \textbf{Time {[}s{]}} \\ \hline
A           & 4        & 1        & 3       & 19.17    \\
B           & 6.5      & 2.5      & 4       & 34.78    \\
C           & 6.37     & 3.63     & 2.74    & 72.53    \\
D           & 4.83     & 7.94     & -3.11   & 300.49   \\
E           & 7.38     & 17.99    & -10.60  & 1110.74  \\
F           & 9.85     & 44.74    & -34.88  & 6289.75  \\ \hline
\end{tabular}
\end{center}
